---
title: "ch4_exercises"
author: "Christopher Chan"
date: "January 23, 2019"
output: rmakrdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
```

## Conceptual
###1
###2

Statquest log regression
```{r}
data <- read_csv("http://archive.ics.uci.edu/ml/machine-learning-databases/heart-disease/processed.cleveland.data", col_names=F)

colnames(data) <- c('age', 'sex', 'cp', 'trestbps', 'chol', 'fbs', 'restecg', 'thalach', 'exang', 'oldpeak', 'slope', 'ca', 'thal', 'hd')
head(data)
str(data)
```

Cleaning the data. Most of the columns got read in as dbl when they should be factors. We are also setting some of the 0/1 to the respective values. Finally we are dropping the NA values, since there are only 6 out of 303 columns with NA.
```{r}
data[data$sex == 0,]$sex <- 'F'
data[data$sex == 1,]$sex <- 'M'

data$ca <- as.integer(data$ca)
data$thal <- as.integer(data$thal)
data$hd <- ifelse(data$hd == 0, 'Healthy', 'Unhealthy')

cols <- c('sex', 'cp', 'fbs', 'restecg', 'exang', 'slope', 'ca', 'thal', 'hd')
data[cols] <- lapply(data[cols], factor)


str(data)
summary(data)

data <- drop_na(data)
```

Creating a cross tabluation for each factor. This makes sure that all levels are relevant in the for the response variable.
```{r}
xtabs(~hd + sex, data)

lapply(data[cols], function(x) xtabs(~hd + x, data))
```

Logistic regression based on sex
```{r}
log_sex <- glm(hd~sex, data, family='binomial')

summary(log_sex)
```

Logisitic regression based on all the predictors.
```{r}
log_all <- glm(hd~., data, family='binomial')

summary(log_all)
```

```{r}
pred <- tibble(prob = log_all$fitted.values,
               hd = data$hd)
pred <- pred[order(pred$prob, decreasing=F),]
pred$rank <- 1:nrow(pred)

ggplot(pred, aes(rank, prob, color=hd)) +
    geom_point()
```
