---
title: "ch3_exercises"
author: "Christoper Chan"
date: "November 23, 2018"
output:
    rmarkdown::github_document:
        pandoc_arg: --webtex
---

#Chapter 3 Exercises

##Conceptual

###1
The null hypothesis is that advertising on TV, radio and newspaper contribute a equal amount to changes in sales. The alternative hypothesis is that this is not true, that in fact at least one of the following: TV, radio and newspaper advertising contribute an non-zero amount to sales. Based on Table 3.4 TV and radio advertising have p-values less than 0.0001, meaning that their coefficients are statistically significant. This implies that their impact is real, and based on their non-negative cofficients, that an increase in spending on TV and radio advertising brings a positive increase in units sold. The large p-value for newspaper implies that it is not significant and does not contribute to sales. 

###2
KNN classifiers return a qualitative value while KNN regression returns a quantitative value, of f(x).

###3
(a) iii
(b) `r 50 + 20*4.0 + 0.07*110 + 35*1 + 0.01*110*4.0 - 10*1*4.0`
(c) False, depends on the p-value.


##Applied

###8
(a) 
```{r, message=FALSE, warning=FALSE}
library(ISLR)
library(MASS)
library(tidyverse)
library(GGally)

summary(Auto)

fit_auto <- lm(mpg~horsepower, data=Auto)
summary(fit_auto)
```

  i. Yes, there is a relationship between mpg and horsepower. This is indicated by the F-statistic that is close to zero. That means we can reject the null hypothesis, that there is no relationship between mpg and horsepower. 
  ii. The residual standard error (RSE) will tell us the quality of the relationship between mpg and horsepower. Because the RSE is 4.906 for 390 DF and the mean for mpg is 23.45, the RSE is `r (4.906/23.45)*100`%.The adjusted $R^2$ is 0.6049, meaning that 60.49% of the variance in mpg can be explained by the horsepower.
  iii. The relationship between mpg and horsepower is negative, given by the negative slope horsepower.
  iv. 
```{r}
predict(fit_auto, data.frame(horsepower=c(98)), interval = 'confidence')

predict(fit_auto, data.frame(horsepower=c(98)), interval = 'prediction')

```

(b)
```{r}
ggplot(Auto, aes(horsepower, mpg)) +
  geom_point() +
  labs(title='LR of horsepower and mpg')
  geom_abline(intercept=39.936, slope=-0.158, color='#E41A1C')
```

(c)
```{r}
par(mfrow=c(2,2))
plot(fit_auto)
```
Plot 1 has a slight curve to it, with most of the points concentrated around 20-30. However, in plot 3 the mean line is roughly linear. Points roughly follow the line for the Normal Q-Q plot and few points are outliers, shown in plot 4.


###9
(a)


```{r}
dim(Auto)
data(Auto)
ggpairs(Auto, columns = 1:8)
```

(b)
```{r}
cor(Auto[,1:8])
```

(c)
```{r}
fit_auto9 <- lm(mpg~.-name, Auto)
summary(fit_auto9)
```
  i. Yes, this is given by the near zeor p-value for the F-statistic.
  ii. There is a relationship for mpg and the following predictor variables: displacement, weight, year, origin. 
  iii. The relatively large coefficient for preditor variable year and the low p-value indicates that there it has a large effect. 

(d) 
```{r}
par(mfrow=c(2,2))
plot(fit_auto9)
```
The residual plot shows a number of outliers at the higher fitted value. On the leverage plot point 14 has a disprportionate amount of leverage.


###10
(a)
```{r}
fit_seats <- lm(Sales~Price + Urban + US, data=Carseats)
summary(fit_seats)
```

(b) Price is statistically significant, with a negative relationship between price and sales. USYes is also statistically significant, indicating a positive relationship between being in the US and sales.

(c) $Sales = \beta_0 + Price*\beta_1 + (1-US)*\beta_2$
(d) Price and USYes are the only predictors whose null hypothesis can be rejected.
(e) 
```{r}
data(Auto)
fit_seats_real <- lm(Sales~Price + US, data=Carseats)
summary(fit_seats_real)
```

(f) Both models, from part (a) and (e), fit the data reasonably well. This is based on the RSE and $R^2$, with the model from part (e) fitting the data slightly better.

(g) 
```{r}
confint(fit_seats_real)
```

(h) 






































