---
title: "ch6_lab2"
author: "Christoper Chan"
date: "December 22, 2018"
output: 
    rmarkdown::github_document:
        pandoc_arg: --webtex
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(forecast)
library(ISLR)
library(leaps)
library(glmnet)
```
#Lab 2: Ridge and Lasso Regression
##6.6.1
Creating a model.matrix of our Hitters data. Because rows with NA are dropped in the model.matrix function the y variable must also drop rows with NA.
```{r}
x <- model.matrix(Salary~., Hitters)[,-1]
y <- Hitters$Salary %>%
    na.omit()
```

Creating an array of length 100 equally spaced distances between 10^-2 and 10^10. This will be our $\lambda$ values that we'll use for the section. We then run ridge regression on our grid.
```{r}
grid <- 10^seq(10,-2, length=100)
ridge_mod <- glmnet(x, y, alpha=0, lambda=grid)
```

This is messing around with different lambda values, showing that high $\lambda$ values yield low coef and low $\lambda$ values give high coef.
```{r}
ridge_mod$lambda[70]
coef(ridge_mod)[,70]
```

Running our ridge regression model on a set $\lambda$, in this case 50.
```{r}
predict(ridge_mod, s=50, type='coefficients')[1:20,]
```






































