---
title: "ch6_exercises"
author: "Christopher Chan"
date: "December 23, 2018"
output: 
    rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(glmnet)
```

##Conceptual
### 1
(a) Best subset should have the lowest RSS because it compares all possible models, while stepwise regression only compares paraments based on the past parameters.
(b) It depends, but most likely best subset should have the lowest RSS.
(c)
    i. True
    ii. True
    iii. False
    iv. False
    v. False
    
### 2
(a) iii. Lasso greatly decreases variance at the cost of increased biases when compared to LSR.  
(b) iii. Same as lasso
(c) ii. Answer

### 3
(a) iv. Increasing s from 0 will cause $\beta$ to increase from 0 to their least squares estimate value.
(b) ii. While lasso provides a decreased variance, it increases bias. once $\beta$ reaches their LR values they overfit the test data.
(c) iii. Variance increases you include more data into the model.
(d) iv. Lasso insures that LR estimate values are reached.
(e) v. By definition irreducible error is model independent.



