---
title: "ch8_exercises"
author: "Christoper Chan"
date: "January 6, 2019"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(gbm)
library(randomForest)
library(ISLR)
library(MASS)
```

##Applied
###7
```{r}
rf_bos <- randomForest(medv~., Boston, ntree=500, mtry=13, importance=T)
plot(rf_bos)
```

So I tried for a good 45 minutes to do this in a for loop and as a function but no luck. The output of randomForest can't be stored in a data.frame. 

TO DO:
Create training and test dataset.
Create different mtry, m=p, m=p/2, m=sqrt(p)



FINALLY! I did it with a for loop. My mistake before was i was putting the mse df in the for loop so the df was being reset each time.
```{r}
tries <- 500

mse <- data.frame(matrix(NA, nrow=tries, ncol=13))
for (i in 1:13){
    a <- randomForest(medv~., Boston, ntree=tries, mtry=i, importance=T)
    mse[i] <- a$mse
}

mse$ntree <- 1:tries
head(mse)
```

Creates a graph of MSE for each mtry. 
```{r}
long <- gather(mse, mtry, value, -ntree)
head(long)


ggplot(long, aes(ntree, value, color=mtry)) +
    geom_line() +
    ylab('MSE')
```

df conversion done with the reshape2 package.
```{r, results='hide'}
library(reshape2)
df <- melt(mse, id.vars='ntree', variable.names='mtry')

View(df)

ggplot(df, aes(ntree, value)) +
    geom_line(aes(color=variable))
```
















