---
title: "ch5_exercises"
author: "Christoper Chan"
date: "January 1, 2019"
output: 
    rmarkdown::github_document:
        pandoc_arg: --webtex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(ISLR)
library(boot)
```

##Conceptual
###1
###2
(a) $(n-j)/n$ That is the probability of not $j$ is the total probability minus the probability of $j$.
(b) $(n-j)/n$ The probabilty is the same as the 1st bootstrap observation. 
(c) Bootstraping observations are independent, so the outcome of each observation does not affect the outcome of the $n$th observation. Using the product rule we simply raise the probability of $j$ not appearing to the $n$th bootstraping observation
(d) $Pr(in) = 1 - Pr(out) = 1 - (1-1/n)^n =$ `r 1-(1-1/5)^5`
(e) `r 1-(1-1/100)^100`
(f) `r 1-(1-1/10000)^10000`
(g) The probabilty drops off quite fast as the number of observations increase. Most are barely above zero.
```{r}
pr <- function(n){
    return (1 - (1-1/n)^n)
}
x <- 1:1e5

pr_x <- tibble(x, pr(x))

ggplot(pr_x, aes(x, pr(x))) +
    geom_point()
```

(h)
```{r}
store <- rep(NA, 1000)
for (i in 1:1000){
    store[i] <- sum(sample(1:100, rep=T)==4) > 0
}

mean(store)
```

###3
